Graphics

### 2020-06-19 individual-cohorts/graphics_t_statistics.Rmd
add AD outgroup and pvclust

# Control vs SCZ
```{r plotb, fig.width = 10, fig.height = 100}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  dplyr::select_if( ~ !all(is.na(.))) %>% 
  dplyr::select(-Comparison)

@@

cor <- cor(df_one)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_one)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```

>>>>

# Control vs SCZ
```{r plotb, fig.width = 10, fig.height = 150}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  dplyr::select_if( ~ !all(is.na(.))) %>% 
  dplyr::select(-Comparison)

@@

cor <- cor(df_two)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_three)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```
